Nail: A practical interface generator for data formats

### 2014-11-26 paper/login/design.tex
pass
typos

 The grammar first calls the zipdir transform on line 2, which finds the magic number and splits the file into
 two streams, one containing the compressed files, the other the directory.  Streams are referred to
 with \cc{\$identifiers}, similar to dependent fields. A C prototype of the \cc{zipdir} transform is
 shown in\ref{fig:zip-transform}. 
\begin{figure}[tb]
\smaller[0.5]
\input{code/zip-eod-xform}
\caption{Signatures of stream transform functions for handling the
end-to-beginning structure of ProtoZIP files.}
\label{fig:zip-transform}
\end{figure}
When parsing input, this will call \cc{zipdir\_parse}, which takes \cc{\$current} -- an implicit
identifier always refering to the stream currently being handled -- and returns \cc{\$files} and
\cc{\$header}. When generating output, this will call \cc{zipdir\_generate}, which appends
\cc{\$files} and \cc{\$header} to \cc{\$current}.

Line 3 then applies the \cc{dir} rule to  the \cc{\$header} stream, passing it the \cc{\$files}
stream. Within \cc{dir}, \cc{\$current} is now \cc{\$header} and input is parsed from and output
generated to that stream. The \cc{dir} rule in turn describes the structure of the directory -- a
magic number and a count field, followed by that many file descripors. Each file descriptor, is then parsed with two
transformations, the standard-library \cc{slice} which describes an offset and a size within another
stream, and the custom \cc{zlib}, which compresses a stream using zlib. Finally, we apply a trivial
grammar (line 14) to the contents.

@@

% For example, we imagine the following grammar could be used to represent
% a sequence of bytes \texttt{data} followed by its CRC32 checksum:

% \begin{verbatim}
% data many uint8; @checksum uint32
% raw_depend @checksum data crc32
% \end{verbatim}

% \noindent
% where \texttt{crc32} is a function supplied by the application, with
% the following signature:

% \begin{verbatim}
% bool crc32(uint32_t *out, uint8_t *in);
% \end{verbatim}

% Because this feature compromises Nail's security guarantees, it should
% only be used in limited circumstances and with carefully prepared checksum
% functions.  This feature is not implemented in the current prototype.

>>>>

 The grammar first calls the zipdir transform on line 2, which finds the magic number and splits the file into
 two streams, one containing the compressed files, the other the directory.  Streams are referred to
 with \cc{\$identifiers}, similar to dependent fields. A C prototype of the \cc{zipdir} transform is
 shown in\ref{fig:zip-transform}. 
\begin{figure}[tb]
\smaller[0.5]
\input{code/zip-eod-xform}
\caption{Signatures of stream transform functions for handling the
end-to-beginning structure of ProtoZIP files.}
\label{fig:zip-transform}
\end{figure}
When parsing input, this will call \cc{zipdir\_parse}, which takes \cc{\$current} -- an implicit
identifier always referring to the stream currently being handled -- and returns \cc{\$files} and
\cc{\$header}. When generating output, this will call \cc{zipdir\_generate}, which appends
\cc{\$files} and \cc{\$header} to \cc{\$current}.

Line 3 then applies the \cc{dir} rule to  the \cc{\$header} stream, passing it the \cc{\$files}
stream. Within \cc{dir}, \cc{\$current} is now \cc{\$header} and input is parsed from and output
generated to that stream. The \cc{dir} rule in turn describes the structure of the directory -- a
magic number and a count field, followed by that many file descriptors. Each file descriptor, is then parsed with two
transformations, the standard-library \cc{slice} which describes an offset and a size within another
stream, and the custom \cc{zlib}, which compresses a stream using zlib. Finally, we apply a trivial
grammar (line 14) to the contents.

@@
